---
title: "Chapter 3 Data Analysis Plan"
author: "Nichole Breeland"
date: "20/12/2019"
output: html_document
fig_width: 6 
fig_height: 4 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#required packages
library(e1071)
library(tidyverse)
library(haven)
library(pixiedust)
library(ggfortify)
library(ggplot2)
library(car)
library(Hmisc)
library(corrplot)
library(MASS)
library(lavaanPlot)
library(lavaan)
library(gee)
library(lme4)
library(lmerTest)
library(doBy)
library(geepack)
```
```{r main dataframe creation, include = FALSE}
#Read in main data file
pp.data = read.csv("ORCA+Parent_AnalysesOnly.csv", stringsAsFactors = FALSE)
#Scientific notation off
options(scipen = 999)
#888 recoded as missing/NA
pp.data[pp.data == 888] <- NA
#999 recoded as missing/NA
pp.data[pp.data == 999] <- NA
#Demographic data file
demo.df <- read.csv("Demographic_ORCA+Peer.csv", stringsAsFactors = FALSE)
#demographics excluding study out participants
so.demo.df <- demo.df[which(demo.df$P4_InOut==1),]
```
```{r p4 peer warm up social context scoring, include = FALSE}
#Afilliation scores - T1, T2, T1T2
pp.data$WU_Afill_T1 <- rowMeans(subset(pp.data, select = c("WU_Afill_Set1", 
                                                           "WU_Afill_Set2", "WU_Afill_Set3")), na.rm = TRUE)
pp.data$WU_Afill_T2 <- rowMeans(subset(pp.data, select = c("WU_Afill_Set4", 
                                                           "WU_Afill_Set5", "WU_Afill_Set6")), na.rm = TRUE)
pp.data$WU_Afill_T1T2 <- rowMeans(subset(pp.data, select = c("WU_Afill_Set1", 
                                                           "WU_Afill_Set2", "WU_Afill_Set3", "WU_Afill_Set4", 
                                                           "WU_Afill_Set5", "WU_Afill_Set6")), na.rm = TRUE)
#Antagonistic scores - T1, T2, T1T2
pp.data$WU_Antag_T1 <- rowMeans(subset(pp.data, select = c("WU_Antag_Set1", 
                                                           "WU_Antag_Set2", "WU_Antag_Set3")), na.rm = TRUE)
pp.data$WU_Antag_T2 <- rowMeans(subset(pp.data, select = c("WU_Antag_Set4", 
                                                           "WU_Antag_Set5", "WU_Antag_Set6")), na.rm = TRUE)
pp.data$WU_Antag_T1T2 <- rowMeans(subset(pp.data, select = c("WU_Antag_Set1", 
                                                           "WU_Antag_Set2", "WU_Antag_Set3", "WU_Antag_Set4", 
                                                           "WU_Antag_Set5", "WU_Antag_Set6")), na.rm = TRUE)

#Engagement scores - T1, T2, T1T2
pp.data$WU_Eng_T1 <- rowMeans(subset(pp.data, select = c("WU_Eng_Set1", 
                                                           "WU_Eng_Set2", "WU_Eng_Set3")), na.rm = TRUE)
pp.data$WU_Eng_T2 <- rowMeans(subset(pp.data, select = c("WU_Eng_Set4", 
                                                           "WU_Eng_Set5", "WU_Eng_Set6")), na.rm = TRUE)
pp.data$WU_Eng_T1T2 <- rowMeans(subset(pp.data, select = c("WU_Eng_Set1", 
                                                           "WU_Eng_Set2", "WU_Eng_Set3", "WU_Eng_Set4", 
                                                           "WU_Eng_Set5", "WU_Eng_Set6")), na.rm = TRUE)

#Joint coordinated engagement - T1, T2, T1T2
pp.data$WU_JCE_T1 <- rowMeans(subset(pp.data, select = c("WU_JCE_Set1", 
                                                           "WU_JCE_Set2", "WU_JCE_Set3")), na.rm = TRUE)
pp.data$WU_JCE_T2 <- rowMeans(subset(pp.data, select = c("WU_JCE_Set4", 
                                                           "WU_JCE_Set5", "WU_JCE_Set6")), na.rm = TRUE)
pp.data$WU_JCE_T1T2 <- rowMeans(subset(pp.data, select = c("WU_JCE_Set1", 
                                                           "WU_JCE_Set2", "WU_JCE_Set3", "WU_JCE_Set4", 
                                                           "WU_JCE_Set5", "WU_JCE_Set6")), na.rm = TRUE)

#Contribution 
pp.data$WU_Contrib <- rowMeans(subset(pp.data, select = c("WU_Contrib_Set4", 
                                                           "WU_Contrib_Set5", "WU_Contrib_Set6")), na.rm = TRUE)
```
```{r p4 peer robot task social context scoring, include = FALSE}
#Afilliation 
pp.data$RT_Afill <- rowMeans(subset(pp.data, select = c("RT_Afill_Set1_FINAL", "RT_Afill_Set2_FINAL", "RT_Afill_Set3_FINAL", "RT_Afill_Set4_FINAL", "RT_Afill_Set5_FINAL", "RT_Afill_Set6_FINAL", "RT_Afill_Set7_FINAL", "RT_Afill_Set8_FINAL", "RT_Afill_Set9_FINAL", "RT_Afill_Set10_FINAL")), na.rm = TRUE)

#Antagonism
pp.data$RT_Antag <- rowMeans(subset(pp.data, select = c("RT_Antag_Set1_FINAL", "RT_Antag_Set2_FINAL", "RT_Antag_Set3_FINAL", "RT_Antag_Set4_FINAL", "RT_Antag_Set5_FINAL", "RT_Antag_Set6_FINAL", "RT_Antag_Set7_FINAL", "RT_Antag_Set8_FINAL", "RT_Antag_Set9_FINAL", "RT_Antag_Set10_FINAL")), na.rm = TRUE)

#Engagement
pp.data$RT_Eng <- rowMeans(subset(pp.data, select = c("RT_Eng_Set1_FINAL", "RT_Eng_Set2_FINAL", "RT_Eng_Set3_FINAL", "RT_Eng_Set4_FINAL", "RT_Eng_Set5_FINAL", "RT_Eng_Set6_FINAL", "RT_Eng_Set7_FINAL", "RT_Eng_Set8_FINAL", "RT_Eng_Set9_FINAL", "RT_Eng_Set10_FINAL")), na.rm = TRUE)

#Joint coordinated engagement
pp.data$RT_JCE <- rowMeans(subset(pp.data, select = c("RT_JCE_Set1_FINAL", "RT_JCE_Set2_FINAL", "RT_JCE_Set3_FINAL", "RT_JCE_Set4_FINAL", "RT_JCE_Set5_FINAL", "RT_JCE_Set6_FINAL", "RT_JCE_Set7_FINAL", "RT_JCE_Set8_FINAL", "RT_JCE_Set9_FINAL", "RT_JCE_Set10_FINAL")), na.rm = TRUE)
```
```{r p4 success (latency y/n), responding and initiating score y/n scoring, include = FALSE}
pp.data$Initiate_yn_3s[pp.data$Initiate_freq_3s == 0] <- 0
pp.data$Initiate_yn_3s[pp.data$Initiate_freq_3s > 0] <- 1
pp.data$Initiate_yn_0s[pp.data$Initiate_freq_0s == 0] <- 0
pp.data$Initiate_yn_0s[pp.data$Initiate_freq_0s > 0] <- 1
pp.data$Respond_yn_3s[pp.data$Respond_freq_3s == 0] <- 0
pp.data$Respond_yn_3s[pp.data$Respond_freq_3s > 0] <- 1
pp.data$Respond_yn_0s[pp.data$Respond_freq_0s == 0] <- 0
pp.data$Respond_yn_0s[pp.data$Respond_freq_0s > 0] <- 1
pp.data$Latency_3sec_yn[pp.data$Latency_3sec >= 0] <- 1
pp.data$Latency_3sec_yn[pp.data$Initiate_freq_3s == 0
                        & pp.data$Respond_freq_3s == 0] <- 0
```
```{r p4 afill/antag y/n scoring for warm up and robot task, include = FALSE}
pp.data$WU_Afill_yn_T1[pp.data$WU_Afill_T1 == 1] <- 0
pp.data$WU_Afill_yn_T1[pp.data$WU_Afill_T1 > 1] <- 1
pp.data$WU_Afill_yn_T2[pp.data$WU_Afill_T2 == 1] <- 0
pp.data$WU_Afill_yn_T2[pp.data$WU_Afill_T2 > 1] <- 1
pp.data$WU_Afill_yn_T1T2[pp.data$WU_Afill_T1T2 == 1] <- 0
pp.data$WU_Afill_yn_T1T2[pp.data$WU_Afill_T1T2 > 1] <- 1
pp.data$WU_Antag_yn_T1[pp.data$WU_Antag_T1 == 1] <- 0
pp.data$WU_Antag_yn_T1[pp.data$WU_Antag_T1 > 1] <- 1
pp.data$WU_Antag_yn_T2[pp.data$WU_Antag_T2 == 1] <- 0
pp.data$WU_Antag_yn_T2[pp.data$WU_Antag_T2 > 1] <- 1
pp.data$WU_Antag_yn_T1T2[pp.data$WU_Antag_T1T2 == 1] <- 0
pp.data$WU_Antag_yn_T1T2[pp.data$WU_Antag_T1T2 > 1] <- 1
pp.data$RT_Afill_yn[pp.data$RT_Afill == 1] <- 0
pp.data$RT_Afill_yn[pp.data$RT_Afill > 1] <- 1
pp.data$RT_Antag_yn[pp.data$RT_Antag == 1] <- 0
pp.data$RT_Antag_yn[pp.data$RT_Antag > 1] <- 1
```
```{r demographic variables coding, include = FALSE}

#SES - Highest education level achieved all participants
#none
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 0 
                       & so.demo.df$Parent_otherqual_spec == 0 
                       | is.na(so.demo.df$Parent_otherqual_spec)] <- 1

#6th form or less/other
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 1 
                       | so.demo.df$Parent_HighestSchoolQual == 2 
                       | so.demo.df$Parent_HighestSchoolQual == 4 
                       & so.demo.df$Parent_otherqual_spec == 0 
                       | is.na(so.demo.df$Parent_otherqual_spec)] <- 2

#7th form only
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 3 
                       & so.demo.df$Parent_otherqual_spec == 0 
                       | is.na(so.demo.df$Parent_otherqual_spec)] <- 3

#Bachelors/Dip
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 0 
                       | so.demo.df$Parent_HighestSchoolQual == 1 
                       | so.demo.df$Parent_HighestSchoolQual == 2 
                       | so.demo.df$Parent_HighestSchoolQual == 3 
                       & so.demo.df$Parent_otherqual_spec == 1] <- 4

#Post grad
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 0 
                       | so.demo.df$Parent_HighestSchoolQual == 1 
                       | so.demo.df$Parent_HighestSchoolQual == 2 
                       | so.demo.df$Parent_HighestSchoolQual == 3 
                       & so.demo.df$Parent_otherqual_spec == 2 
                       | so.demo.df$Parent_otherqual_spec == 3 ] <- 5

#Other Tertiary
so.demo.df$Edu.all_Cat[so.demo.df$Parent_HighestSchoolQual == 0 
                       | so.demo.df$Parent_HighestSchoolQual == 1 
                       | so.demo.df$Parent_HighestSchoolQual == 2 
                       | so.demo.df$Parent_HighestSchoolQual == 3 
                       & so.demo.df$Parent_otherqual_spec == 4 ] <- 6

so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 1] <- "None"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 2] <- "6th form or less"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 3] <- "7th form"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 4] <- "Bachelors/PgDip"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 5] <- "Honours, Masters, PhD"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 6] <- "Other tertiary"
so.demo.df$Edu.all_label[is.na(so.demo.df$Edu.all_Cat)] <- "Unknown/Missing"
so.demo.df$Edu.all_label[so.demo.df$Edu.all_Cat == 999] <- "Unknown/Missing"
table(so.demo.df$Edu.all_label)


#Child ethnicity
#Ethnicity categories
#NZE = 1
#NZE/Maori =2
#NZE/Asian = 3
#NZE/Other = 4
#--
#Other = 5
#Asian = 7
#Pacific = 8
#Other European = 9
#NZE/O-E = 10
#NZE-Pacific = 11
#NZE-MELAA = 12
#Asian-OE = 13
#Maori-OE = 14
#MELLAA-OE = 15

#NZE
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0] <- 1

#NZE/Maori =2
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 1 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0] <- 2

#NZE/Asian = 3
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 1 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0] <- 3


#NZE/Other/O-E = 4
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 1 
               & so.demo.df$Other == 1] <- 4

#Other = 5
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 1] <- 5

#Asian = 7
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 1 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0]<- 7


#Pacific = 8
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 1
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0] <- 8


#Other European = 9
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 1 
               & so.demo.df$Other == 0] <- 9

#NZE-Pacific = 11
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 1
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 0 
               & so.demo.df$Other == 0] <- 11


#NZE-MELAA = 12
so.demo.df$Eth_Cat[so.demo.df$NZEur == 1 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 1 & so.demo.df$OtherEur == 0
               & so.demo.df$Other == 0] <- 12


#Asian-OE = 13
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 1 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 1
               & so.demo.df$Other == 0] <- 13

#Maori-OE = 14
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 1 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 0 & so.demo.df$OtherEur == 1
               & so.demo.df$Other == 0] <- 14

#MELLAA-OE = 15
so.demo.df$Eth_Cat[so.demo.df$NZEur == 0 & so.demo.df$Maori == 0 
               & so.demo.df$Asian == 0 & so.demo.df$Pacific == 0
               & so.demo.df$MidEastLatAmAfrican == 1 & so.demo.df$OtherEur == 1
               & so.demo.df$Other == 0] <- 15

so.demo.df$Eth_Cat[is.na(so.demo.df$Eth_Cat)] <- 16

so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 1] <- "NZE"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 7] <- "Asian"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 8] <- "Pacific"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 9] <- "Other European (OE)"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 5] <- "Other"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 2] <- "NZE/Maori"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 3] <- "NZE/Asian"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 4] <- "NZE/Other/OE"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 11] <- "NZE-Pacific"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 12] <- "NZE_MELAA"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 13] <- "Asian-OE"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 14] <- "Maori-OE"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 15] <- "MELLAA-OE"
so.demo.df$Eth_CatLabel[so.demo.df$Eth_Cat == 16] <- "2 or more/Missing = 21"
#Missing total is 21 (visual check), 29 = 2 or more
```

### Variable transformation information
```{r transformed variable scoring}
pp.data$Latency_3sec_Trans <- pp.data$Latency_3sec^(1/3)
pp.data$Initiate_freq_3s_LogTrans <- log(pp.data$Initiate_freq_3s + 1)
pp.data$Respond_freq_3s_LogTrans <- log(pp.data$Respond_freq_3s + 1)
pp.data$WU_JCE_T1_Trans <- pp.data$WU_JCE_T1^(1/3)
pp.data$WU_JCE_T2_Trans <- pp.data$WU_JCE_T2^(1/3)
pp.data$WU_Contrib_Trans <- pp.data$WU_Contrib^(1/2)
pp.data$RT_JCE_Trans <- pp.data$RT_JCE^(1/3) #Outliers present will windsorize 
```
```{r data subsets and outlier management, include = FALSE}
#Dataset restructure (individual to dyad)

#Subset to include shared variables and p4 study in only (excludes p4 study out and participant number)

indiv.df <- pp.data[which(pp.data$P4_InOut==1),]
indiv.df <- indiv.df[c(-1)]

### Outlier management ###

#Robot Task JCE Transformed
mean(indiv.df$RT_JCE_Trans, na.rm = TRUE)
#1.124617
#indiv.df
sd(indiv.df$RT_JCE_Trans, na.rm = TRUE)
#0.1201474
3*0.1201474 #3xSD
#0.3604422
0.3604422+1.124617 #3xSD+MEAN
#Scores greater than 1.485059 are outliers
sort(indiv.df$RT_JCE_Trans)
#Outlier replacement and variable recreation
indiv.df$RT_JCE_Trans_OR <- indiv.df$RT_JCE_Trans
indiv.df$RT_JCE_Trans_OR[indiv.df$RT_JCE_Trans_OR >= 1.485059] <- 1.481248
#6 values replaced with next highest value


# Dyad structure data
dyad <- indiv.df %>% 
  rename(dyad_id = Dyad_Number) %>% 
  rename_all(tolower)

#dyad.df is the final dyadic dataframe
#data with _o suffix is orca data _p is peer data
dyad.df <- dyad %>%
  arrange(dyad_id) %>%
  gather(key,value,-dyad_id,-p4_inout,-gender,
         -parent_type_p5,-pcg_p5,-p4_inout_comments, 
         -parent_type_p1, -pcg_p1, -dyad_level, -rt_tt_sec, 
         -latency_3sec, -latency_3sec_trans, 
         -latency_3sec_yn) %>%
  mutate(dyad_level = ifelse(dyad_level == 1,"o","p")) %>%
  unite(new_key,key,dyad_level,sep = "_",remove=T) %>%
  spread(new_key,value)

dyad.df <- dyad.df %>%
  arrange(dyad_id)
```
```{r p4 frequency of cooperative actions dyad scoring, include = FALSE}
for (i in 1:nrow(dyad.df)) {
  dyad.df$Freq_CA_p4[i] <- max(dyad.df[i,c("initiate_freq_3s_o","initiate_freq_3s_p","respond_freq_3s_o", "respond_freq_3s_p")])
}
```
```{r P4 Peers age difference scoring, include = FALSE}
dyad.df$age_p4_diff <- abs(dyad.df$age_p4_o - dyad.df$age_p4_p)
```

### Results Summary  
  
The present study has the following aims: 
  
1.) determine the extent to which the warm up social context (affiliation, antagonism, and jce) relates to the social context in the robot task  
2.) determine the extent to which the warm up social context relates to cooperative ability in the robot task (latency to success, initiating behaviours, responding behaviours)  
3.) determine the extent to which the robot task social context relates to cooperative ability in the robot task   
  
In order to answer the aformentioned research questions, we conducted tests on both the individual set of data, where both the ORCA and the peer are treated as individual participants, and dyadic set of data.  
  
**Primary analyses findings:**
  
* (Analysis Type: GEE) Any display of antagonistic behaviour during the first 1:30 of the warm up is associated with antagonistic behaviour in the robot task by a liklihood of 223% (or 3.27x).
* (Analysis Type: GEE) Displays of afilliative behaviours during the first 1:30 of warm up are associated with displays of initiating behaviours by a liklihood of 81% (or 1.81x)
* (Analysis Type: GEE) Any display of antagonistic behaviour during the first 1:30 of the warm up is associated with displays of responding behaviours by a liklihood of 129% (2.29x), but the effect significance goes away with gender is controlled for within the model.
* (Analysis Type: GEE) Every one-unit increase in contribution to toy tidy scores is associated with a 1% increase in liklihood of successful goal completion and a 13% (or 1.13x) increased liklihood of engaging in at least 1 responding behaviour.
* (Analysis Type: GEE) Being affiliative is associated with a liklihood of being successful (i.e., completing the goal) on the robot task by 4%.
* (Analysis Type: GEE) For every 1 unit increase in JCE, the liklihood of being successful on the robot task increases by .85 or 14% and the liklihood of engaging in an initiating behaviour increases by 2.45x or 145%, and the liklihood of engaging in a responding behaviour increases by 2.79x or 179%.
  
### Results notes, considerations, and decisions 
* Latency to success (continuous variable) isn't a great measure and breaks most LMM. This is, of course, because of the low number of dyads who were able to achieve the goal. Instead - to fully capture what is happening I created a quasi success variable. If the dyad had a latency score and thus achieved the goal, they recieved a score of 1 for variable: Latency_3sec_yn. If no latency score and this no goal achievement, they recieved a score of zero. I analysed this variable as a binary latency variable with all predictors.
* I have run both generalized linear mixed models for binary variables, however GEE may be more appropriate. The difference? *The basic difference in interpretation is that GLMMs model "individual level effects" (i.e. what is the effect of the predictor variable for a particular person), whereas GEEs model population level trends (i.e. what is the average difference in the outcome between groups with different values of the predictor variables). That is, GLMMs are generally more appropriate if you want to know about effects of an intervention/risk factor/etc. for an individual, whereas GEE are more appropriate for questions of public health. It's a subtle difference, and actually the interpretation is largely the same for linear models, but are different for, e.g., binary or count outcomes. The other main difference is that GEE are not "model based"- that is, they will give you proper p-values, even when your model assumptions are wrong. However, GLMM's are more sensitive to model assumptions.* Several papers note GEE is great for categorical DVs when looking at actor partner effects, etc.
* For P4 PEER Demo data - SES: 64 complete (out of 161), 97 missing. Child ethnicity: 138 complete (out of 161), 23 missing.

  
### Research Questions - Primary Analyses  

#### Warm Up Analyses 
To our knowledge, all of the studies investigating peer cooperation do not take into account what occurs in the "warm up phase" of studies involving child participants. This is alarming and concerning as research shows that first impressions (e.g., an individuals choice in an economic game, such as a public goods or trust game) have an effect on subsequent cooperative actions/contributions between two or more people (Engel et al., 2014; Grueneisen & Tomasello, 2017; see other literature about multi-shot economic games). The Broken Windows Theory (Wilson & Kelling, 1982) suggests that obvious signs of social disorder (e.g., graffiti or broken windows in a neighbourhood) encourages further social disorder/crime. This holds true in lab based experiments as well suggesting that the social situation (e.g., contributions to the greater good) decays if others behave selfishly and are "found out" (Engel et al., 2014). Broken Windows Theory taken together with previous research regarding multiple-shot economic games highlights the need for researchers to explore the social context that two child participants are situated in *before* completing a cooperative task. If cooperation occurs in the initial meeting aka warm up phase, surely this supports later cooperation. Alternatively, if social decay occurs within the warm up phase, research would suggest that this would hinder cooperative success in subsequent tasks. But do 2-year-olds hold grudges?  
  
*Note.* T1 = score for first 1:30, T2 = score for last 1:30
  
##### Warm Up Social Context + Robot Task Social Context
  
* Does warm up affiliation relate to robot task affiliation? **No.**
  
```{r warm up + robot affiliation}
#GEE
#create dataframe with complete observations
df.wu.rt.afill.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                   "RT_Afill_yn", 
                                                   "WU_Afill_yn_T1", 
                                                   "WU_Afill_yn_T2"))
df.wu.rt.afill.gee <- na.omit(df.wu.rt.afill.gee)

wu.rt.afill.gee <- geeglm(RT_Afill_yn ~ WU_Afill_yn_T1 
                          + WU_Afill_yn_T2, 
                          family=binomial,
                          data=df.wu.rt.afill.gee, 
                          id=Dyad_Number, 
                          corstr = "exchangeable", 
                          std.err="san.se") 
summary(wu.rt.afill.gee)
anova(wu.rt.afill.gee)
```
  
* Does warm up antagonism relate to robot task antagonism? **Yes, according to the GEE model, individuals who are antagonistic at T1 of Warm up are 223% or 3.27x more likely to display antagonistic behaviour in the robot task**

```{r warm up + robot antagonism}
#GEE
#create dataframe with complete observations
df.wu.rt.antag.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                   "RT_Antag_yn", 
                                                   "WU_Antag_yn_T1", 
                                                   "WU_Antag_yn_T2"))
df.wu.rt.antag.gee <- na.omit(df.wu.rt.antag.gee)

wu.rt.antag.gee <- geeglm(RT_Antag_yn ~ WU_Antag_yn_T1
                          + WU_Antag_yn_T2, 
                          family=binomial,
                          data=df.wu.rt.antag.gee, 
                          id=Dyad_Number, 
                          corstr = "exchangeable", 
                          std.err="san.se") 
summary(wu.rt.antag.gee)
anova(wu.rt.antag.gee)
```
  
* Does warm up JCE relate to robot task JCE? **No - ran with outliers 'windsorized' and no differences**
  
```{r warm up + robot jce}

#LMM
wu.rt.jce<- lmer(RT_JCE_Trans ~ WU_JCE_T1
                        + WU_JCE_T2
                        + (1|Dyad_Number),
                    data = indiv.df,
                 na.action = na.omit,
                 REML=FALSE)
summary(wu.rt.jce)
#Assumption checks
Plot.wu.rt.jce <- plot(wu.rt.jce)
Plot.wu.rt.jce
qqmath(wu.rt.jce, id=0.05)
```
  
##### Warm Up Social Context + Robot Task Ability
  
* Does warm up affiliation relate to robot task cooperative ability? **According to the GEE model, those who display afilliative behaviours at T1 are 1.81 times more likely to engage in initiating behaviours**
  
```{r warm up affiliation + robot ability}
#Success - GEE
#create dataframe with complete observations
df.wu.rt.lat.t1.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                    "Latency_3sec_yn", 
                                                    "WU_Afill_yn_T1", 
                                                    "WU_Afill_yn_T2"))
df.wu.rt.lat.t1.gee  <- na.omit(df.wu.rt.lat.t1.gee)

wu.rt.lat.t1.gee <- geeglm(Latency_3sec_yn ~ WU_Afill_yn_T1 
                           + WU_Afill_yn_T2, 
                           family=binomial, 
                           data=df.wu.rt.lat.t1.gee, 
                           id=Dyad_Number, 
                           corstr = "exchangeable", 
                           std.err="san.se") 
summary(wu.rt.lat.t1.gee)
anova(wu.rt.lat.t1.gee)

#Initiating Behaviours - GEE
#create dataframe with complete observations
df.wu.rt.init.gee <- subset(indiv.df, select = c ("Dyad_Number",
                                                  "Initiate_yn_3s", 
                                                  "WU_Afill_yn_T1", 
                                                  "WU_Afill_yn_T2", 
                                                  "Gender"))
df.wu.rt.init.gee  <- na.omit(df.wu.rt.init.gee)

wu.rt.init.gee <- geeglm(Initiate_yn_3s ~ WU_Afill_yn_T1 
                         + WU_Afill_yn_T2 
                         + Gender, 
                         family=binomial,
                         data=df.wu.rt.init.gee, 
                         id=Dyad_Number, 
                         corstr = "exchangeable", 
                         std.err="san.se") 
summary(wu.rt.init.gee)
anova(wu.rt.init.gee)
exp(0.5927) #1.81
# 1 -  1.81 = 81% likelihood or 1.81 times more likely

#Responding Behaviours - GEE
#create dataframe with complete observations
df.wu.rt.resp.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                  "Respond_yn_3s", 
                                                  "WU_Afill_yn_T1", 
                                                  "WU_Afill_yn_T2", 
                                                  "Gender", 
                                                  "Age_P4"))
df.wu.rt.resp.gee  <- na.omit(df.wu.rt.resp.gee)

wu.rt.resp.gee <- geeglm(Respond_yn_3s ~ WU_Afill_yn_T1 
                         + WU_Afill_yn_T2 
                         + Gender
                         + Age_P4, 
                         family=binomial,
                         data=df.wu.rt.resp.gee, 
                         id=Dyad_Number, 
                         corstr = "exchangeable", 
                         std.err="san.se") 
summary(wu.rt.resp.gee)
anova(wu.rt.resp.gee)
```
  
* Does warm up antagonism relate to robot task cooperative ability? **No, however antagonism T1 could could increase responding behaviours but this effect is only significant when not controlling for gender (which isn't significant in the model anyway) - according to the GEE**
  
```{r warm up antagonism + robot ability}
#Success - GEE
#create dataframe with complete observations
df.wu.antag.rt.lat.t1.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                          "Latency_3sec_yn", 
                                                          "WU_Antag_yn_T1", 
                                                          "WU_Antag_yn_T2"))
df.wu.antag.rt.lat.t1.gee <- na.omit(df.wu.antag.rt.lat.t1.gee)

wu.antag.rt.lat.t1.gee<- geeglm(Latency_3sec_yn ~ WU_Antag_yn_T1 
                                + WU_Antag_yn_T2, 
                                family=binomial,
                                data=df.wu.antag.rt.lat.t1.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(wu.antag.rt.lat.t1.gee)
anova(wu.antag.rt.lat.t1.gee)

#Initiating Behaviours - GEE
#create dataframe with complete observations
df.wu.antag.rt.init.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                        "Initiate_yn_3s", 
                                                        "WU_Antag_yn_T1", 
                                                        "WU_Antag_yn_T2", 
                                                        "Gender"))
df.wu.antag.rt.init.gee <- na.omit(df.wu.antag.rt.init.gee)

wu.antag.rt.lat.t1.gee<- geeglm(Initiate_yn_3s ~ WU_Antag_yn_T1 
                                + WU_Antag_yn_T2 
                                + Gender, 
                                family=binomial,
                                data=df.wu.antag.rt.init.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(wu.antag.rt.lat.t1.gee)
anova(wu.antag.rt.lat.t1.gee)

# Responding Behaviours - GEE
#create dataframe with complete observations
df.wu.antag.rt.resp.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                        "Respond_yn_3s", 
                                                        "WU_Antag_yn_T1", 
                                                        "WU_Antag_yn_T2", 
                                                        "Gender", 
                                                        "Age_P4"))
df.wu.antag.rt.resp.gee <- na.omit(df.wu.antag.rt.resp.gee)

wu.antag.rt.lat.t1.gee<- geeglm(Respond_yn_3s ~ WU_Antag_yn_T1 
                                + WU_Antag_yn_T2 
                                + Gender 
                                + Age_P4, 
                                family=binomial,
                                data=df.wu.antag.rt.resp.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(wu.antag.rt.lat.t1.gee)
anova(wu.antag.rt.lat.t1.gee)
```  
  
* Does warm up jce relate to robot task cooperative ability? **No**
  
```{r warm up jce + robot ability}
#Success - GEE
df.wu.jce.rt.lat.suc <- subset(indiv.df, select = c ("Dyad_Number", 
                                                     "Latency_3sec_yn", 
                                                     "WU_JCE_T1", 
                                                     "WU_JCE_T2"))
df.wu.jce.rt.lat.suc <- na.omit(df.wu.jce.rt.lat.suc)

wu.jce.rt.lat.suc <- geeglm(Latency_3sec_yn~WU_JCE_T1 
                         + WU_JCE_T2,
                         family=binomial,
                         data=df.wu.jce.rt.lat.suc, 
                         id=Dyad_Number, 
                         corstr = "exchangeable", 
                         std.err="san.se") 
summary(wu.jce.rt.lat.suc)
anova(wu.jce.rt.lat.suc)

# Initiating Behaviours - GEE
#create dataframe with complete observations
df.wu.jce.rt.init <- subset(indiv.df, select = c ("Dyad_Number", 
                                                  "Initiate_yn_3s", 
                                                  "WU_JCE_T1", 
                                                  "WU_JCE_T2", 
                                                  "Gender"))
df.wu.jce.rt.init <- na.omit(df.wu.jce.rt.init)

wu.jce.rt.init <- geeglm(Initiate_yn_3s~WU_JCE_T1
                         +WU_JCE_T2 
                         + Gender, 
                         family=binomial,
                         data=df.wu.jce.rt.init, 
                         id=Dyad_Number, 
                         corstr = "exchangeable", 
                         std.err="san.se") 
summary(wu.jce.rt.init)
anova(wu.jce.rt.init)

# Responding Behaviours - GEE
#create dataframe with complete observations
df.wu.jce.rt.resp <- subset(indiv.df, select = c ("Dyad_Number", 
                                                  "Respond_yn_3s", 
                                                  "WU_JCE_T1", 
                                                  "WU_JCE_T2", 
                                                  "Gender", 
                                                  "Age_P4"))
df.wu.jce.rt.resp <- na.omit(df.wu.jce.rt.resp)

wu.jce.rt.resp <- geeglm(Respond_yn_3s ~ WU_JCE_T1 
                         + WU_JCE_T2 
                         + Gender 
                         + Age_P4, 
                         family=binomial,
                         data=df.wu.jce.rt.resp, 
                         id=Dyad_Number, 
                         corstr = "exchangeable", 
                         std.err="san.se") 
summary(wu.jce.rt.resp)
anova(wu.jce.rt.resp)
```  
  
* Does warm up contribution to toy tidy relate to robot task cooperative ability?  **According to the GEE - those who demonstrate increased contribution to toy tidy are .99x more likely/1% more likely to complete the end goal successfully atleast once and 13% (or 1.13x) more likely to engage in at least 1 responding behaviour**
  
```{r warm up contrib + robot ability}

#Success - GEE
#create dataframe with complete observations
df.wu.contrib.rt.lat.t2.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                            "Latency_3sec_yn", 
                                                            "WU_Contrib"))
df.wu.contrib.rt.lat.t2.gee <- na.omit(df.wu.contrib.rt.lat.t2.gee)

wu.contrib.rt.lat.t2.gee <- geeglm(Latency_3sec_yn ~ WU_Contrib, 
                                   family=binomial,
                                   data=df.wu.contrib.rt.lat.t2.gee, 
                                   id=Dyad_Number, 
                                   corstr = "exchangeable", 
                                   std.err="san.se") 
summary(wu.contrib.rt.lat.t2.gee)
anova(wu.contrib.rt.lat.t2.gee)
exp(-0.001445)


#Initiating Behaviours - GEE
#create dataframe with complete observations
df.wu.init.rt.lat.t2.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                         "Initiate_yn_3s", 
                                                         "WU_Contrib", 
                                                         "Gender"))
df.wu.init.rt.lat.t2.gee <- na.omit(df.wu.init.rt.lat.t2.gee)

wu.init.rt.lat.t2.gee <- geeglm(Initiate_yn_3s ~ WU_Contrib 
                                + Gender, 
                                family=binomial,
                                data=df.wu.init.rt.lat.t2.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(wu.init.rt.lat.t2.gee)
anova(wu.init.rt.lat.t2.gee)


#Responding behaviours - GEE
#create dataframe with complete observations
df.wu.resp.rt.lat.t2.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                         "Respond_yn_3s", 
                                                         "WU_Contrib", 
                                                         "Gender", 
                                                         "Age_P4"))
df.wu.resp.rt.lat.t2.gee <- na.omit(df.wu.resp.rt.lat.t2.gee)

wu.resp.rt.lat.t2.gee <- geeglm(Respond_yn_3s ~ WU_Contrib 
                                + Age_P4 
                                + Gender, 
                                family=binomial,
                                data=df.wu.resp.rt.lat.t2.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(wu.resp.rt.lat.t2.gee)
anova(wu.resp.rt.lat.t2.gee)
exp(0.1204)
```  
  
##### Robot Social Context + Robot Social Context
  
* Does robot affiliation relate to robot task cooperative ability? **Yes, according to the GEE, being affiliative is associated with a liklihood of being successful on the robot task by 4%.**
  
```{r robot afill + robot ability}
#Success - GEE
#create dataframe with complete observations
df.rtsc.rt.lat.afill.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                         "Latency_3sec_yn", 
                                                         "RT_Afill_yn"))
df.rtsc.rt.lat.afill.gee <- na.omit(df.rtsc.rt.lat.afill.gee)

rtsc.rt.lat.afill.gee <- geeglm(Latency_3sec_yn ~ RT_Afill_yn, 
                                family=binomial,
                                data=df.rtsc.rt.lat.afill.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(rtsc.rt.lat.afill.gee)
anova(rtsc.rt.lat.afill.gee)
exp(-0.0422) #.96


#Initiating behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.init.afill.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                          "Initiate_yn_3s", 
                                                          "RT_Afill_yn", 
                                                          "Gender"))
df.rtsc.rt.init.afill.gee <- na.omit(df.rtsc.rt.init.afill.gee)

rtsc.rt.init.afill.gee <- geeglm(Initiate_yn_3s ~ RT_Afill_yn 
                                 + Gender, 
                                 family=binomial,
                                 data=df.rtsc.rt.init.afill.gee, 
                                 id=Dyad_Number, 
                                 corstr = "exchangeable", 
                                 std.err="san.se") 
summary(rtsc.rt.init.afill.gee)
anova(rtsc.rt.init.afill.gee)

#Responding behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.resp.afill.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                          "Respond_yn_3s", 
                                                          "RT_Afill_yn", 
                                                          "Gender", 
                                                          "Age_P4"))
df.rtsc.rt.resp.afill.gee <- na.omit(df.rtsc.rt.resp.afill.gee)

rtsc.rt.resp.afill.gee <- geeglm(Respond_yn_3s ~ RT_Afill_yn 
                                 + Gender 
                                 + Age_P4, 
                                 family=binomial,
                                 data=df.rtsc.rt.resp.afill.gee, 
                                 id=Dyad_Number, 
                                 corstr = "exchangeable", 
                                 std.err="san.se") 
summary(rtsc.rt.resp.afill.gee)
anova(rtsc.rt.resp.afill.gee)
```
  
* Does robot antgonism relate to robot task cooperative ability? **No**
  
```{r robot antag + robot ability}

#Success - GEE
#create dataframe with complete observations
df.rtsc.rt.lat.antag.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                         "Latency_3sec_yn", 
                                                         "RT_Antag_yn"))
df.rtsc.rt.lat.antag.gee <- na.omit(df.rtsc.rt.lat.antag.gee)

rtsc.rt.lat.antag.gee <- geeglm(Latency_3sec_yn ~ RT_Antag_yn, 
                                family=binomial,
                                data=df.rtsc.rt.lat.antag.gee, 
                                id=Dyad_Number, 
                                corstr = "exchangeable", 
                                std.err="san.se") 
summary(rtsc.rt.lat.antag.gee)
anova(rtsc.rt.lat.antag.gee)

#Initiating behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.init.antag.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                          "Initiate_yn_3s", 
                                                          "RT_Antag_yn", 
                                                          "Gender"))
df.rtsc.rt.init.antag.gee <- na.omit(df.rtsc.rt.init.antag.gee)

rtsc.rt.init.antag.gee <- geeglm(Initiate_yn_3s ~ RT_Antag_yn 
                                 + Gender, 
                                 family=binomial,
                                 data=df.rtsc.rt.init.antag.gee, 
                                 id=Dyad_Number, 
                                 corstr = "exchangeable", 
                                 std.err="san.se") 
summary(rtsc.rt.init.antag.gee)
anova(rtsc.rt.init.antag.gee)


#Responding behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.resp.antag.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                          "Respond_yn_3s", 
                                                          "RT_Antag_yn", 
                                                          "Gender", 
                                                          "Age_P4"))
df.rtsc.rt.resp.antag.gee <- na.omit(df.rtsc.rt.resp.antag.gee)

rtsc.rt.resp.antag.gee <- geeglm(Respond_yn_3s ~ RT_Antag_yn 
                                 + Gender 
                                 + Age_P4, 
                                 family=binomial,
                                 data=df.rtsc.rt.resp.antag.gee, 
                                 id=Dyad_Number, 
                                 corstr = "exchangeable", 
                                 std.err="san.se") 
summary(rtsc.rt.resp.antag.gee)
anova(rtsc.rt.resp.antag.gee)
```
  
* Does robot jce relate to robot task cooperative ability? **Yes - according to the GEE models for everyone 1 unit increase in JCE, the liklihood of being successful on the robot task increases by .86 or 14% and the liklihood of engaging in an initiating behaviour increases by 2.45x or 145% and the liklihood of engaging in a responding behaviour increases by 2.79x or 179%**
  
```{r robot jce + robot ability}
#Success- GEE
#create dataframe with complete observations
df.rtsc.rt.lat.jce.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                       "Latency_3sec_yn", 
                                                       "RT_JCE"))
df.rtsc.rt.lat.jce.gee <- na.omit(df.rtsc.rt.lat.jce.gee)

rtsc.rt.lat.jce.gee <- geeglm(Latency_3sec_yn ~ RT_JCE, 
                              family=binomial,
                              data=df.rtsc.rt.lat.jce.gee, 
                              id=Dyad_Number, 
                              corstr = "exchangeable", 
                              std.err="san.se") 
summary(rtsc.rt.lat.jce.gee)
anova(rtsc.rt.lat.jce.gee)
exp(-0.1522)

#Initiating behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.init.jce.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                        "Initiate_yn_3s", 
                                                        "RT_JCE", 
                                                        "Gender"))
df.rtsc.rt.init.jce.gee <- na.omit(df.rtsc.rt.init.jce.gee)

rtsc.rt.init.jce.gee <- geeglm(Initiate_yn_3s ~ RT_JCE 
                               + Gender, 
                               family=binomial,
                               data=df.rtsc.rt.init.jce.gee, 
                               id=Dyad_Number, 
                               corstr = "exchangeable", 
                               std.err="san.se") 
summary(rtsc.rt.init.jce.gee)
anova(rtsc.rt.init.jce.gee)
exp(0.898) #2.45

#Responding behaviours - GEE
#create dataframe with complete observations
df.rtsc.rt.resp.jce.gee <- subset(indiv.df, select = c ("Dyad_Number", 
                                                        "Respond_yn_3s", 
                                                        "RT_JCE", 
                                                        "Gender", 
                                                        "Age_P4"))
df.rtsc.rt.resp.jce.gee <- na.omit(df.rtsc.rt.resp.jce.gee)

rtsc.rt.resp.jce.gee <- geeglm(Respond_yn_3s ~ RT_JCE 
                               + Gender 
                               + Age_P4, 
                               family=binomial,
                               data=df.rtsc.rt.resp.jce.gee, 
                               id=Dyad_Number, 
                               corstr = "exchangeable", 
                               std.err="san.se") 
summary(rtsc.rt.resp.jce.gee)
anova(rtsc.rt.resp.jce.gee)
exp(1.0273) #262 
```
  
### Research Questions - Follow Up Analyses 
  
The following analyses are exploratory. Due to significant effects in the models that included gender - we decided to run an additional model with gender as a moderator. None of the primary analyses met the criteria for further mediation analyses.
  
### Research Questions - Secondary Analyses  
  
#### Individual Level Analyses (ALL) 
  
*Note. These are all individual level analyses where the ORCA and peer are treated as individual participants*
  
##### Warm Up Social Context
  
* Are there differences between T1 and T2 for all social context warm up variables? **Yes, for all social context variables except antagonism - all subsequent analyses comparing the warm up to other variables will be split between T1 and T2**
  
```{r warm up social context time sampling differences}
#test for differences between warm up T1 and T2 averages for all social context binary variables

##affiliation differences - yes
#contingency table
afill.wu.tab <- table(indiv.df$WU_Afill_yn_T1, indiv.df$WU_Afill_yn_T2)
afill.wu.tab
#chi-square test - sig
chisq.test(afill.wu.tab)

##antagonism differences - yes
#contingency table
antag.wu.tab <- table(indiv.df$WU_Antag_yn_T1, indiv.df$WU_Antag_yn_T2)
antag.wu.tab
#chi-square test - sig
chisq.test(antag.wu.tab)

##jce differences - yes

#JCE subset
## jce score - warm up
WU.jce <- subset(indiv.df, select=c("WU_JCE_T1", "WU_JCE_T2"))
WU.jce <- gather(WU.jce, time, score, WU_JCE_T1:WU_JCE_T2, factor_key=TRUE)
WU.jce <- na.omit(WU.jce)
#wilcox test

wilcox.test(score ~ time, data = WU.jce, paired=FALSE)
group_by(WU.jce, time) %>%
  summarise(
    count = n(),
    median = median(score, na.rm = TRUE),
    IQR = IQR(score, na.rm = TRUE)
  )
```
  
* Are there gender differences for warm up social context variables? **Yes, there is a gender difference in the affiliation score between genders for T1**
  
```{r warm up social context gender differences}
#gender differences for warm up affiliation T1 binary variable

##affiliation differences - yes
#contingency table
afill.wu.gen.tab <- table(indiv.df$WU_Afill_yn_T1, indiv.df$Gender)
afill.wu.gen.tab 
#chi-square test - sig
chisq.test(afill.wu.gen.tab)

#gender differences for warm up affiliation T2 - No
afill2.wu.gen.tab <- table(indiv.df$WU_Afill_yn_T2, indiv.df$Gender)
afill2.wu.gen.tab 
#chi-square test 
chisq.test(afill2.wu.gen.tab)

##gender differences for warm up antagonism T1 - No
antag.wu.gen.tab <- table(indiv.df$WU_Antag_yn_T1, indiv.df$Gender)
antag.wu.gen.tab 
#chi-square test - 
chisq.test(antag.wu.gen.tab)

##gender differences for warm up antagonism T2 - No
antag2.wu.gen.tab <- table(indiv.df$WU_Antag_yn_T2, indiv.df$Gender)
antag2.wu.gen.tab 
#chi-square test 
chisq.test(antag2.wu.gen.tab)

##gender differences for warm up jce T1 - no
wilcox.test(WU_JCE_T1 ~ Gender, data = indiv.df, paired=FALSE)
#on transformed variable - no
t.test(WU_JCE_T1_Trans ~ Gender, data = indiv.df, paired=FALSE)
##gender differences for warm up jce T2
wilcox.test(WU_JCE_T2 ~ Gender, data = indiv.df, paired=FALSE)
#on transformed variable - no
t.test(WU_JCE_T2_Trans ~ Gender, data = indiv.df, paired=FALSE)
##gender differences for warm up contribution
wilcox.test(WU_Contrib ~ Gender, data = indiv.df, paired=FALSE)
#on transformed variable - no
t.test(WU_Contrib_Trans ~ Gender, data = indiv.df, paired=FALSE)
```
  
* Is there a relationship between age and warm up social context variables? **No**
  
```{r warm up social context age differences}

#association between age and warm up affiliation t1 - no
t.test(indiv.df$Age_P4 ~ indiv.df$WU_Afill_yn_T1)

#association between age and warm up affiliation t2 - no
t.test(indiv.df$Age_P4 ~ indiv.df$WU_Afill_yn_T2)

#association between age and warm up antagonism t1 - no
t.test(indiv.df$Age_P4 ~ indiv.df$WU_Antag_yn_T1)

#association between age and warm up antagonism t2 - no
t.test(indiv.df$Age_P4 ~ indiv.df$WU_Antag_yn_T2)

#association between age and warm up jce t1 - no
age.wu.jce.t1 <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_JCE_T1, method = 'spearman')
age.wu.jce.t1

#association between age and warm up jce t1 transformed - no
age.wu.jce.t1.trans <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_JCE_T1_Trans, method = 'spearman')
age.wu.jce.t1.trans


#association between age and warm up jce t2 - no
age.wu.jce.t2 <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_JCE_T2, method = 'spearman')
age.wu.jce.t2

#association between age and warm up jce t2 transformed - no
age.wu.jce.t2.trans <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_JCE_T2_Trans, method = 'spearman')
age.wu.jce.t2.trans

#association between age and warm up contributions - no
age.wu.contrib <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_Contrib, method = 'spearman')
age.wu.contrib

#association between age and warm up contributions transformed - no
age.wu.contrib.trans <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$WU_Contrib_Trans, method = 'spearman')
age.wu.contrib.trans
```

##### Robot Social Context
  
* Are there gender differences for robot social context variables? **No**
  
```{r robot social context gender differences}
#gender differences for robot task affiliation - no

afill.rt.gen.tab <- table(indiv.df$RT_Afill_yn, indiv.df$Gender)
afill.rt.gen.tab
#chi-square test 
chisq.test(afill.rt.gen.tab)

##gender differences for robot task antagonism - no
antag.rt.gen.tab <- table(indiv.df$RT_Antag_yn, indiv.df$Gender)
antag.rt.gen.tab
#chi-square test 
chisq.test(antag.rt.gen.tab)

##gender differences for robot task jce
wilcox.test(RT_JCE ~ Gender, data = indiv.df, paired=FALSE)

##gender differences for robot task jce transformed - no
t.test(RT_JCE_Trans ~ Gender, data = indiv.df, paired=FALSE)

##gender differences for robot task jce transformed + windsorized - no
t.test(RT_JCE_Trans_OR ~ Gender, data = indiv.df, paired=FALSE)
```
  
* Is there a relationship between age and robot social context variables? **No**
  
```{r robot social context age differences}

#association between age and warm robot task affiliation - no
t.test(indiv.df$Age_P4 ~ indiv.df$RT_Afill_yn)

#association between age and robot task antagonism - no
t.test(indiv.df$Age_P4 ~ indiv.df$RT_Antag_yn)

#association between age and warm up jce - no
age.rt.jce <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$RT_JCE, method = 'spearman')
age.rt.jce

#association between age and warm up jce transformed - no
age.rt.jce.trans <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$RT_JCE_Trans, method = 'spearman')
age.rt.jce.trans

#association between age and warm up jce transformed + windsorized - no
age.rt.jce.trans.or <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$RT_JCE_Trans_OR, method = 'spearman')
age.rt.jce.trans.or
```
  
#### Robot Cooperative Ability
  
* Does participant age correlate latency to success? **No**
  
```{r correlation between age for orca and peer and latency to success}
#association for age of peer and orca and predicting latency
age.latency <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$Latency_3sec, method = 'pearson')
age.latency

#association for age of peer and orca and predicting latency (transcribed)
age.latency.trans <- cor.test(x = indiv.df$Age_P4, 
                       y = indiv.df$Latency_3sec_Trans, method = 'pearson')
age.latency.trans

#association for age of peer and orca success - latency binary
age.latency.yn <- t.test(indiv.df$Age_P4 ~ indiv.df$Latency_3sec_yn)
age.latency.yn
```
  
* Does the age difference between the participants correlate to latency to success **No**
  
```{r correlation between age difference within the dyad and latency to success}
#correlation between age difference and latency scores
agediff.latency.df <- subset(dyad.df, select = c("age_p4_diff","latency_3sec", "latency_3sec_trans"))
agediff.latency.df <- na.omit(agediff.latency.df)
agediff.latency.corr <- cor.test(x = agediff.latency.df$age_p4_diff, 
                       y = agediff.latency.df$latency_3sec, method = 'spearman')
agediff.latency.corr 

#transformed variable
agediff.latency.corr.trans <- cor.test(x = agediff.latency.df$age_p4_diff, 
                       y = agediff.latency.df$latency_3sec_trans, method = 'pearson')
agediff.latency.corr.trans 

#binary variable
agediff.latency.yn <- t.test(dyad.df$age_p4_diff ~ dyad.df$latency_3sec_yn)
agediff.latency.yn 
```
  
* Are there age differences between groups of children who did and did NOT engage in initiating/responding behaviours? **Yes, but only for the 'responded group.' In other words, the group of children who exhibited a cooperative handle response behaviour were older than the group who did not.**
  
```{r ttest for age differences for cooperative ability behaviours}
#because many (~100) participants DONT have a latency score, 
#a ttest is conducted to see if there is an age effect for age 
#on if the child engaged in any initiating/responding behaviours.

#age at p4 and initiate (y/n)
t.test(indiv.df$Age_P4~indiv.df$Initiate_yn_3s)

#age at p4 and respond (y/n)
t.test(indiv.df$Age_P4~indiv.df$Respond_yn_3s)
```
  
* Are there gender differences in latency to success scores? **No**
  
```{r gender and robot latency to success}
#gender differences for robot latency to success
wilcox.test(latency_3sec ~ gender, data = dyad.df, paired=FALSE)
#transformed variable
t.test(latency_3sec_trans ~ gender, data = dyad.df, paired=FALSE)
#binary variable
succ.yn.gender.tab <- table(dyad.df$latency_3sec_yn, dyad.df$gender)
succ.yn.gender.tab
#chi-square test 
chisq.test(succ.yn.gender.tab)
```
  
* Are there gender differences between whether or not the child engaged in initating behaviours? **Yes**
  
```{r gender and robot initiate yn}
#gender differences for if the child initated a cooperation sequence ever
init.yn.gender.tab <- table(indiv.df$Initiate_yn_3s, indiv.df$Gender)
init.yn.gender.tab
#chi-square test 
chisq.test(init.yn.gender.tab)
```
  
* Are there gender differences between whether or not the child engaged in responding behaviours? **Yes**
  
```{r gender and robot respond yn}
#gender differences for if the child responded a cooperation sequence ever
resp.yn.gender.tab <- table(indiv.df$Respond_yn_3s, indiv.df$Gender)
resp.yn.gender.tab
#chi-square test 
chisq.test(resp.yn.gender.tab)
```

### Research Questions - Exploratory Analyses  
This section includes analyses that we may not have strong hypotheses for (due to lack of theory or previous research) but are still important to test.  

#### Exploratory/Checks
* Are there correlations between cooperative ability and social context on the robot task?
```{r RT cooperation correlation matrix, include = FALSE }
#Note rr_tt_sec is the length of robot task interaction in seconds
RT_ca.sc.df <- subset(dyad.df, select = c("rt_tt_sec", "initiate_freq_3s_o", "initiate_freq_3s_p",
                                          "respond_yn_3s_o", "respond_yn_3s_p","initiate_yn_3s_o",
                                          "initiate_yn_3s_p","respond_yn_3s_o", 
                                          "respond_yn_3s_p","rt_afill_yn_o", "rt_afill_yn_p",
                                          "rt_antag_yn_o", "rt_antag_yn_p", "rt_afill_o", "rt_afill_p",
                                          "rt_antag_o", "rt_antag_p", "rt_jce_o", "rt_jce_p", "rt_eng_o",
                                          "rt_eng_p"))

RT_ca.sc.cor <- cor(RT_ca.sc.df, use = "complete.obs")
round(RT_ca.sc.cor, 2)
RT_ca.sc.cor2 <- rcorr(as.matrix(RT_ca.sc.df))
RT_ca.sc.cor2
RT_ca.sc.cor2$r
# Extract p-values
RT_ca.sc.cor2$P

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
```
```{r RT cooperation table and matrix corr, set-options, echo=FALSE, cache=FALSE}
options(width = 500)

flattenCorrMatrix(RT_ca.sc.cor2$r, RT_ca.sc.cor2$P)
corrplot(RT_ca.sc.cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

```


```{r}
test <- subset(dyad.df_pcgm.p5, select = c("dyad_id", "Freq_CA_p4","rt_afill_o", "rt_afill_p", "respond_freq_3s_o", "respond_freq_3s_p", "initiate_freq_3s_p", "initiate_freq_3s_o", "wu_afill_t1t2_o", "wu_afill_t1t2_p"))
write.csv(test, "dyadicdata.csv")
```
```{r}
dyadic.wu.rt.sc <- subset(dyad.df, select = c ("dyad_id", "gender", "latency_3sec", "Freq_CA_p4", "age_p4_diff", "age_p4_o", "age_p4_p", "wu_afill_yn_t1_o", "wu_afill_yn_t2_o", "wu_antag_yn_t1_o", "wu_antag_yn_t2_o", "wu_jce_t1_o", "wu_jce_t2_o", "wu_contrib_o", "wu_afill_yn_t1_p", "wu_afill_yn_t2_p", "wu_antag_yn_t1_p", "wu_antag_yn_t2_p", "wu_jce_t1_p", "wu_jce_t2_p", "wu_contrib_p", "rt_afill_yn_o", "rt_antag_yn_o", "rt_jce_o", "rt_afill_yn_p", "rt_antag_yn_p", "rt_jce_p", "respond_freq_3s_o", "respond_yn_3s_o", "respond_yn_3s_p", "respond_freq_3s_p", "initiate_freq_3s_o", "initiate_yn_3s_o", "initiate_yn_3s_p", "initiate_freq_3s_p"))

write.csv(dyadic.wu.rt.sc, "dyadic.sc.wu.rt.csv")
```
 
## Variables & Descriptions


### Individual Level Descriptives

#### Age of all participants
* Type: Continuous  
* Function: Control, IV 
```{r Participant age on all P4 study in participants}
with(indiv.df, hist(Age_P4,breaks = 20,
                   xlab = "age (months)",
                   main = "hist participant (N = 294) age"))
mean(indiv.df$Age_P4, na.rm = TRUE)
sd(indiv.df$Age_P4, na.rm = TRUE)
median(indiv.df$Age_P4, na.rm = TRUE)
range(indiv.df$Age_P4, na.rm = TRUE)
#number of observations NAs removed
sum(!is.na(indiv.df$Age_P4))
```

#### Age difference
* Type: Continuous  
* Function: IV  
* Description: The difference in age (in months) between the ORCA child and peer child
 
```{r Age difference in months - dyad}
with(dyad.df, hist(age_p4_diff,breaks = 20,
                   xlab = "Age difference",
                   main = "hist of dyad age differences"))
mean(dyad.df$age_p4_diff, na.rm = TRUE)
sd(dyad.df$age_p4_diff, na.rm = TRUE)
range(dyad.df$age_p4_diff, na.rm = TRUE)
```
  
#### Gender of all participants
* Type: Categorical  
* Function: Control, IV  
```{r Participant gender}
table(indiv.df$Gender)
#1 = male, 2 = female
```
#### Social Context Variables
  
Warm Up Social Context
  
**Note. Due to lack of variability and normality issues we have chosen to analyse affiliation and antagonism variables as binary. JCE is cube root transformed while contributions is square root transformed - when these variables are used as predictors, original variables are to be included in the model**
```{r warm up social context individual level}

#Affiliation T1
with(indiv.df, hist(WU_Afill_yn_T1,breaks = 2,
                   xlab = "yes or no affiliation",
                   main = "hist of y/n afilliation \n at time 1"))
table(indiv.df$WU_Afill_yn_T1)

#Afilliation Time 2
with(indiv.df, hist(WU_Afill_yn_T2,breaks = 2,
                   xlab = "yes or no affiliation",
                   main = "hist of y/n affilliation \n at time 2"))
table(indiv.df$WU_Afill_yn_T2)

#antagonism T1
with(indiv.df, hist(WU_Antag_yn_T1,breaks = 2,
                   xlab = "yes or no antagonism",
                   main = "hist of y/n antagonism \n at time 1"))
table(indiv.df$WU_Antag_yn_T1)

#Antagonism Time 2
with(indiv.df, hist(WU_Antag_yn_T2,breaks = 2,
                   xlab = "yes or no antagonism",
                   main = "hist of y/n antagonism \n at time 2"))
table(indiv.df$WU_Antag_yn_T2)

#JCE T1 - untransformed - #!OUTLIERS PRESENT
with(indiv.df, hist(WU_JCE_T1,breaks = 5,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_JCE_T1, na.rm = TRUE)
sd(indiv.df$WU_JCE_T1, na.rm = TRUE)
range(indiv.df$WU_JCE_T1, na.rm = TRUE)

#JCE T1 - cube root transformed - no outliers
with(indiv.df, hist(WU_JCE_T1_Trans,breaks = 5,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_JCE_T1_Trans, na.rm = TRUE)
sd(indiv.df$WU_JCE_T1_Trans, na.rm = TRUE)
range(indiv.df$WU_JCE_T1_Trans, na.rm = TRUE)


#JCE T2 - untransformed - #!OUTLIERS PRESENT
with(indiv.df, hist(WU_JCE_T2,breaks = 5,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_JCE_T2, na.rm = TRUE)
sd(indiv.df$WU_JCE_T2, na.rm = TRUE)
range(indiv.df$WU_JCE_T2, na.rm = TRUE)

#JCE T2 - cube root transformed - no outliers
with(indiv.df, hist(WU_JCE_T2_Trans,breaks = 5,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_JCE_T2_Trans, na.rm = TRUE)
sd(indiv.df$WU_JCE_T2_Trans, na.rm = TRUE)
range(indiv.df$WU_JCE_T2_Trans, na.rm = TRUE)

#contribution scores - untransformed - no outliers
with(indiv.df, hist(WU_Contrib,breaks = 10,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_Contrib, na.rm = TRUE)
sd(indiv.df$WU_Contrib, na.rm = TRUE)
range(indiv.df$WU_Contrib, na.rm = TRUE)

#contribution scores - square root tansformed - no outliers
with(indiv.df, hist(WU_Contrib_Trans,breaks = 5,
                   xlab = "",
                   main = ""))
mean(indiv.df$WU_Contrib_Trans, na.rm = TRUE)
sd(indiv.df$WU_Contrib_Trans, na.rm = TRUE)
range(indiv.df$WU_Contrib_Trans, na.rm = TRUE)
```
  
Robot Task Social Context
  
**Note. Due to lack of variability and normality issues we have chosen to analyse affiliation and antagonism variables as binary, JCE has outliers present and normality issues. 2 new variables are created where one is cube root transformed and another is cube root transfromed AND windsorized - transformed variables will only be used when variables appear as DVs in the model.**
```{r robot task social context individual level}
#Affiliation RT
with(indiv.df, hist(RT_Afill_yn,breaks = 2,
                   xlab = "yes or no affiliation",
                   main = "hist of y/n afilliation"))
table(indiv.df$RT_Afill_yn)

#Antag RT
with(indiv.df, hist(RT_Antag_yn,breaks = 2,
                   xlab = "yes or no antagonism",
                   main = "hist of y/n antagonism"))
table(indiv.df$RT_Antag_yn)

#JCE RT - untransformed - #OUTLIERS PRESENT
with(indiv.df, hist(RT_JCE,breaks = 10,
                   xlab = "",
                   main = ""))
mean(indiv.df$RT_JCE, na.rm = TRUE)
sd(indiv.df$RT_JCE, na.rm = TRUE)
range(indiv.df$RT_JCE, na.rm = TRUE)

#JCE RT - cube root transformed - #OUTLIERS PRESENT
with(indiv.df, hist(RT_JCE_Trans,breaks = 10,
                   xlab = "",
                   main = ""))
mean(indiv.df$RT_JCE_Trans, na.rm = TRUE)
sd(indiv.df$RT_JCE_Trans, na.rm = TRUE)
range(indiv.df$RT_JCE_Trans, na.rm = TRUE)

#JCE RT - cube root transformed - outliers (> 3SD+MEAN windsorized)
with(indiv.df, hist(RT_JCE_Trans_OR,breaks = 10,
                   xlab = "",
                   main = ""))
mean(indiv.df$RT_JCE_Trans_OR, na.rm = TRUE)
sd(indiv.df$RT_JCE_Trans_OR, na.rm = TRUE)
range(indiv.df$RT_JCE_Trans_OR, na.rm = TRUE)

```

#### Length of Robot Task Interaction
* Type: Continuous  
* Function: IV  
* Description: How long (in seconds) the dyad interacted with the robot task. Task began once the experimenter finished instructions ("remember you have to push both handles at the same time) and task finished once the experimenter started to say "I know lets look at a new game"
```{r Dyad time on task - robot task}
with(dyad.df, hist(rt_tt_sec,breaks = 20,
                   xlab = "seconds",
                   main = "hist of robot task length"))
mean(dyad.df$rt_tt_sec, na.rm = TRUE)
sd(dyad.df$rt_tt_sec, na.rm = TRUE)
range(dyad.df$rt_tt_sec, na.rm = TRUE)
```
  
#### Latency to first success  
* Type: Continuous  
* Function: DV  
* Description: Between-dyad variable (joint measure of cooperation). How long did it take for the dyad to hold the handles completely down within 3s of one another  CALCULATED VIA INTERACT  
```{r Latency to success - dyad - untransformed}
with(dyad.df, hist(latency_3sec,breaks = 20,
                   xlab = "Latency to success in seconds",
                   main = "hist dyad latency"))
mean(dyad.df$latency_3sec, na.rm = TRUE)
sd(dyad.df$latency_3sec, na.rm = TRUE)
range(dyad.df$latency_3sec, na.rm = TRUE)
#number of observations NAs removed
sum(!is.na(dyad.df$latency_3sec))
```
  
* Because the data is heavily skewed, a cube root transformation may be appropriate - this is also appropriate for variables contianing 0 values. (see McElwain et al., 2016)

```{r latency to success cube transformed}

with(dyad.df, hist(latency_3sec_trans, breaks = 5,
                   xlab = "Latency to success in cube root seconds",
                   main = "hist dyad latency - \n cube root transformed"))
```

* As so few dyads achieved the goal (< 50/140) and thus obtained a latency to success score, we have created a binary variable based upon the latency score. If the child achieved the goal and thus had a valid latency score - they scored a 1 and if they did not achieve the goal and thus did not earn a latency score they scored a 0. This variable may be refered to as "success" (y/n)
  
```{r latency to success yn}

with(dyad.df, hist(latency_3sec_yn, breaks = 2,
                   xlab = "Goal success",
                   main = "hist dyad success - \n i.e. goal achieved"))
table(dyad.df$latency_3sec_yn)
```
  
#### Frequency of cooperative action sequences  
* Type: Continuous  
* Function: DV  
* Description: Between-dyad variable (joint measure of cooperation). How many times did the dyad hold the handles completely down within 3s of one another  CALCULATED VIA INTERACT  
```{r Freq CA sequences dyad}
with(dyad.df, hist(Freq_CA_p4,breaks = 10,
                   xlab = "# cooperative action sequences",
                   main = "hist dyad cooperative actions"))
mean(dyad.df$Freq_CA_p4, na.rm = TRUE)
sd(dyad.df$Freq_CA_p4, na.rm = TRUE)
range(dyad.df$Freq_CA_p4, na.rm = TRUE)
table(dyad.df$Freq_CA_p4)
#number of observations NAs removed
sum(!is.na(dyad.df$Freq_CA_p4))
```

#### Descriptive Statistics for entire dataset - indiv structure
  
Means and SD for initiating behaviours (3sec)
  
**Despite the strongest transformation for both variables, normality issues still present. Therefore we have chosen to classify as a binary variable (y/n)**
```{r Initiating behaviours entire sample -3s}
#Untransformed
with(indiv.df, hist(Initiate_freq_3s ,breaks = 5,
                   xlab = "# initiating behaviours",
                   main = "hist dyad initiating actions"))
mean(indiv.df$Initiate_freq_3s, na.rm = TRUE)
sd(indiv.df$Initiate_freq_3s, na.rm = TRUE)


#Transformed
with(indiv.df, hist(Initiate_freq_3s_LogTrans ,breaks = 5,
                   xlab = "# log initiating behaviours",
                   main = "hist dyad initiating actions log"))
mean(indiv.df$Initiate_freq_3s_LogTrans, na.rm = TRUE)
sd(indiv.df$Initiate_freq_3s_LogTrans, na.rm = TRUE)


#Binary
with(indiv.df, hist(Initiate_yn_3s ,breaks = 2,
                   xlab = "# y or n initiating behaviours",
                   main = "hist dyad initiating actions yes or no"))
table(indiv.df$Initiate_yn_3s)
```
  
Means and SD for responding behaviours (3sec)
  
```{r Responding behaviours entire sample -3s}
#Untransformed
with(indiv.df, hist((Respond_freq_3s),breaks = 10,
                   xlab = "# responding behaviours",
                   main = "hist dyad responding actions"))
mean(indiv.df$Respond_freq_3s, na.rm = TRUE)
sd(indiv.df$Respond_freq_3s, na.rm = TRUE)

#Transformed
with(indiv.df, hist(Respond_freq_3s_LogTrans,breaks = 10,
                   xlab = "# responding behaviours",
                   main = "hist dyad responding actions"))
mean(indiv.df$Respond_freq_3s_LogTrans, na.rm = TRUE)
sd(indiv.df$Respond_freq_3s_LogTrans, na.rm = TRUE)

#Binary
with(indiv.df, hist(Respond_yn_3s ,breaks = 2,
                   xlab = "# y or n responding behaviours",
                   main = "hist dyad responding actions yes or no"))
table(indiv.df$Respond_yn_3s)
```

Means and SD for initiating behaviours (0sec)
```{r Initiating behaviours entire sample -0s}
mean(pp.data$Initiate_freq_0s, na.rm = TRUE)
sd(pp.data$Initiate_freq_0s, na.rm = TRUE)
```
Means and SD for responding behaviours (0sec)
```{r Responding behaviours entire sample -0s}
mean(pp.data$Respond_freq_0s, na.rm = TRUE)
sd(pp.data$Respond_freq_0s, na.rm = TRUE)
```
  
### Sample Demographic data
  
#### Child Ethnicity
* Type: Categorical  
* Function: Descriptive 
```{r ethnicity}
table(so.demo.df$Eth_CatLabel)
#2+ and missing is combined.
#21 are missing so 29 = 2+ eth.
```
 

#### SES   
* Type: Categorical  
* Function: Descriptive 
* Description: Groups based upon parent highest level of education - 1 = no high school completion, 2 = completed high school, 3 = completed something beyond high school  
```{r SES}
table(so.demo.df$Edu.all_label)
```

